Modelling BCG vaccination in the UK

### 2019-12-11 rmds/05-evidence-policy-change.Rmd
dodd minor corrections up to 6

---
output:
  pdf_document: default
  html_document: default
---
# Reassessing the evidence for universal school-age Bacillus Calmette Guerin (BCG) vaccination in England and Wales {#sutherland}

>>>>

---
output:
  pdf_document: default
  html_document: default
---
# Reassessing the evidence for universal school-age BCG vaccination in England and Wales {#sutherland}
